### 2018-01-14 includes/introduction.tex
Applying first round of feedback.

    Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and practically useful.

    Moreover a standard input language, SMT-LIB, has been developed, and many mature solvers support it.

>>>>

    Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and practically useful. Moreover a standard input language, \smt{}, has been developed and many mature solvers support it.

    In this paper, we present the following contributions:

    \begin{enumerate}
        \item StringFuzzG and StringFuzzX: a generator and transformer of \smt{} string and regex problems.
        \item Experiments on generated inputs that show evidence of poor performance in \us{} and \cvc{}.
        \item A recommended fix to \us{} that alleviates the poor performance.
        \item A large suite of \smt{} string and regex problems we generated with \fuzzer{}.
    \end{enumerate}

### 2018-01-14 includes/problems.tex
Applying first round of feedback.

    Along with this paper we present several suites of ready-made problems produced by StringFuzz. These suites can be found on \problemRepo{}.

@@

        Most of these problem sets either have a dedicated generator in \generator{}, or are variations of one. While it is likely that some of the pre-made suites will be immediately useful in analysing a solver, we also found that mass randomisation was helpful in finding some bugs, and we encourage this pattern as well. \generator{} is designed to be used in an exploratory fashion, and the following usage has helped us in our own experiments:

@@

    \subsection{Results}

>>>>

    We generated several suites of string and regex problems using \fuzzer{}, and they are available at \problemRepo{}. They are described in more detail below.

@@

        Most of these problem sets either have a dedicated generator in \generator{}, or are variations of one. While it is likely that some of the pre-made suites will be immediately useful in analysing a solver, we also found that mass randomisation was helpful in finding some bugs, and we encourage this pattern as well. \generator{} is designed to be used in an exploratory fashion. For example the following usage has helped us find bugs in \us{}:

@@

    \subsection{Bugs Found}

### 2018-01-14 includes/recommendation.tex
Applying first round of feedback.

\section{Experiments}

    Here we present two particular sets of problems generated by \fuzzer{}: Eager-Hard and Lazy-Hard. These two problem sets were unique in their ability to elicit poor performance in one solver, but not another. Full details of test scripts, configurations, and problems that were used in the experiment can be found in the Appendix.

    \textbf{TODO:}

    \begin{enumerate}
        \item supply machine environment description
        \item supply install scripts that produce trace builds
        \item supply test scripts that invoke the solvers and produce traces
    \end{enumerate}

\section{Results}

    \subsection{Performance on Lazy-Hard}

        On this problem set \cvc{} did poorly, but \us{} did well. The graphs in figure X show the performance results for both solvers.

        \cvc{} showed the following behaviour in its log file:

        \begin{enumerate}
            \item Loads all facts
            \item Flattens concats
            \item Computes equivalence classes
            \item Discovers conflict early
                {\scriptsize\begin{verbatim}
CONFLICT: Eq engine conflict : (and (= "woof" (str.++ "woof" lsym_5 lsym_5 lsym_5 lsym_5
lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5)) (= "" lsym_5)
(= "" var3) (= "" var5) (= "" var7) (= "" var9) (= "" var11) (= "" var13) (= "" var15)
(= "" var17) (= "" var19) (= "" var21) (= "" var23) (= "" var25) (= "" var27) (= "" var29)
(= "" var30) (= (str.++ "woof" var3 var5 var7 var9 var11 var13 var15 var17 var19 var21
var23 var25 var27 var29 var30) (str.++ "meow" var43 var45 var47 var49 var51 var53 var55
var57 var59 var61 var63 var65 var67 var69 var70)) (= "" var43) (= "" var45) (= "" var47)
(= "" var49) (= "" var51) (= "" var53) (= "" var55) (= "" var57) (= "" var59) (= "" var61)
(= "" var63) (= "" var65) (= "" var67) (= "" var69) (= "" var70) (= "meow" (str.++ "meow"
lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5
lsym_5 lsym_5)))
                \end{verbatim}}
            \item Gets caught doing some sort of check
            \item Infers inequality
        \end{enumerate}

        \us{} showed the following behaviour in its log file:

        \begin{enumerate}
            \item loads all facts
            \item immediately spots inconsistency:
                {\scriptsize\begin{verbatim}
-------- [str] new_eq_check ../src/smt/theory_str.cpp:1864 ---------
checking whether (str.++ "woof" var2) and (str.++ "meow" var42) can be equal
------------------------------------------------
-------- [str] new_eq_check ../src/smt/theory_str.cpp:1867 ---------
inconsistency detected: (str.++ "woof" var2) cannot be equal to (str.++ "meow" var42)
------------------------------------------------
-------- [str] assert_axiom ../src/smt/theory_str.cpp:179 ---------
asserting (not (= (str.++ "woof" var2) (str.++ "meow" var42)))
------------------------------------------------
                \end{verbatim}}
        \end{enumerate}

        \textbf{TODO:}

        \begin{enumerate}
            \item \us{} cactus plot
            \item \cvc{} cactus plot
            \item comparison plot
        \end{enumerate}

    \subsection{Eager-Hard}

        On this problem set \cvc{} did well, but \us{} did poorly. The graphs in figure X show the performance results for both solvers.

        \cvc{} showed the following behaviour in its log file:

        \begin{enumerate}
            \item Loads all facts
            \item Flattens concats
            \item Computes equivalence classes
            \item Finds solution
        \end{enumerate}

        \us{} showed the following behaviour in its log file:

        \begin{enumerate}
            \item Loads all facts
            \item Tries assigning solution by "dragging" it across the variables
            \item Creates a ton of equivalence classes
            \item Gets caught comparing equivalence classes
            \item Finds solution
        \end{enumerate}

        \textbf{TODO:}

        \begin{enumerate}
            \item \us{} cactus plot
            \item \cvc{} cactus plot
            \item comparison plot
        \end{enumerate}

    \subsection{Concats-Extracts}

        No data on this yet.

    \subsection{Regex Suite}

        No data on this yet.

\section{Analysis}

    This section presents our analysis of the observed behaviour of \cvc{} and \us{} on Lazy-Hard and Eager-Hard problems.

    \subsection{Lazy-Hard}

        Here is why \cvc{} does poorly and \us{} does well.

    \subsection{Eager-Hard}

        Here is why \cvc{} does well and \us{} does poorly.

@@

    \textbf{TODO:}

    \begin{enumerate}
        \item definition of partial order
        \item definition of current class relation
        \item definition of class relation under partial order
    \end{enumerate}

>>>>

@@

    % TODO:
    % - definition of partial order
    % - definition of current class relation
    % - definition of class relation under partial order

### 2018-01-14 includes/stringfuzz.tex
Applying first round of feedback.

    This section presents \fuzzer{}. \fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyse \smt{} string problems. Its source code repository is available at \sourceRepo{}. It can either be installed from source, or from the Python PIP package repository.

    \subsection{Generators: \generator{}}

        \generator{} is available as a command-line tool, \texttt{stringfuzzg}. It supports several generators and options that control its output. The generators it implements are:

@@

    \subsection{Transformers: \transformer{}}

        \transformer is available as a command-line tool, \texttt{stringfuzzx}. It supports several transformers and options that control its output and input. The transformers it implements are:

    \subsection{Utilities}

        Some utilities are also provided with \fuzzer{}. They are: \texttt{stringstats}, \texttt{stringmerge}, \texttt{smtparse}, and \texttt{smtscan}.

            \item[\texttt{stringstats}] \hfill \\ \\
                This tool takes as input an \smt{} problem, and outputs its properties. The properties are:

@@

            \item[\texttt{stringmerge}] \hfill \\ \\
                This tool takes as input two \smt{} problems and combines them into one problem.

@@

    \subsection{Architecture}

        Should I describe its architecture?

>>>>

    This section describes the fuzzer \fuzzer{}. \fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyse \smt{} string problems. Its source code repository is available at \sourceRepo{}. It can either be installed from source, or from the Python PIP package repository.

    The \fuzzer{} code is organised to be easily extended with more generators and transformers. It is also implemented in the spirit of a Unix "filter", to be easily integrated into other tools. For example, the outputs of generators can be piped directly into transformers, and transformers can be chained to produce a tuned stream of challenging inputs to a solver.

    Below are descriptions of the tools that come with \fuzzer{}:

        \item[\texttt{stringfuzzg}] \hfill \\
            This tool generates \smt{} problems. It supports several generators and options that control its output. The generators it implements are:

@@

        \item[\texttt{stringfuzzx}] \hfill \\
            This tool transforms \smt{} problems.. It supports several transformers and options that control its output and input. The transformers it implements are:

            \begin{itemize}
                \item fuzz
                \item graft
                \item multiply
                \item nop
                \item reverse
                \item rotate
                \item translate
                \item unprintable
            \end{itemize}

        \item[\texttt{stringstats}] \hfill \\
            This tool takes as input an \smt{} problem, and outputs its properties. The properties are:

@@

        \item[\texttt{stringmerge}] \hfill \\
            This tool takes as input two \smt{} problems and combines them into one problem.

@@
